---
title: "Assignment Group EDA"
output: html_notebook
---

 

```{r}
library(readr)
data = read_csv("C:\\Users\\Hafiz Asyraaf\\OneDrive\\Desktop\\BSD3433 EDA\\Group project\\ceramic.csv")
data
```




```{r}
## Fit a model with up to third order interactions.
results=aov(strength~(speed+rate+grit+direction+batch)^3,data=data)
summary(results)
```
Based on the summary above, it shown some of significant factor and non-significant factor in from the dataset

Significant :-

-speed
-speed:grit
-speed:direction
-speed:batch
-rate:grit
-rate:batch
-grit:batch
-direction:batch
-speed:rate:grit 
-speed:rate:batch
-speed:grit:direction
-speed:grit:batch
-speed:direction:batch     
-rate:grit:direction       
-rate:grit:batch           
-rate:direction:batch      
-grit:direction:batch 

```{r}
## Remove non-significant terms from the stepwise model.
redmod = aov(formula = strength ~ speed + rate + grit + direction + 
            batch + speed:rate + speed:grit + speed:direction +  
            rate:direction + grit:direction + direction:batch + 
            speed:rate:direction, data = data)
summary(redmod)
```
```{r}
library(gplots)
```
MAIN EFFECT

```{r}
plotmeans(strength~speed,xlab="Factor speed",ylab="Strength", main="Main effect Plot",barcol="blue",data=data)
```

```{r}
plotmeans(strength~rate,xlab="Factor Rate",ylab="Strength", main="Main effect Plot",barcol="blue",data=data)
```
```{r}
plotmeans(strength~grit,xlab="Factor Grit",ylab="Strength", main="Main effect Plot",barcol="blue",data=data)
```
```{r}
plotmeans(strength~direction,xlab="Factor Direction",ylab="Strength", main="Main effect Plot",barcol="blue",data=data)
```

```{r}
plotmeans(strength~batch,xlab="Factor Batch",ylab="Strength", main="Main effect Plot",barcol="blue",data=data)
```


ITERATION PLOT

speed : Rate
```{r}
interaction.plot(x.factor = data$speed, #x-axis variable
                 trace.factor = data$rate, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "speed",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "rate")
```


speed : Grit
```{r}
interaction.plot(x.factor = data$speed, #x-axis variable
                 trace.factor = data$grit, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "speed",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "grit")
```

speed:Direction

```{r}
interaction.plot(x.factor = data$speed, #x-axis variable
                 trace.factor = data$direction, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "speed",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "direction")
```

speed : Batch
```{r}
interaction.plot(x.factor = data$speed, #x-axis variable
                 trace.factor = data$batch, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "speed",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "batch")
```

Rate : Grit
```{r}
interaction.plot(x.factor = data$rate, #x-axis variable
                 trace.factor = data$grit, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "rate",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "grit")
```

Rate:Direction
```{r}
interaction.plot(x.factor = data$rate, #x-axis variable
                 trace.factor = data$direction, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "rate",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "direction")
```

```{r}
interaction.plot(x.factor = data$rate, #x-axis variable
                 trace.factor = data$batch, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "rate",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "batch")
```

Grit : Direction
```{r}
interaction.plot(x.factor = data$grit, #x-axis variable
                 trace.factor = data$direction, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "grit",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "direction")
```
Grit : Batch
```{r}
interaction.plot(x.factor = data$grit, #x-axis variable
                 trace.factor = data$batch, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "grit",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "batch")
```

Direction : Batch
```{r}
interaction.plot(x.factor = data$direction, #x-axis variable
                 trace.factor = data$batch, #variable for lines
                 response = data$strength, #y-axis variable
                 fun = median, #metric to plot
                 ylab = "strength",
                 xlab = "direction",
                 col = c("pink", "blue"),
                 lty = 1, #line type
                 lwd = 2, #line width
                 trace.label = "batch")
```

```{r}
results$effects
```

```{r}
effects <- abs(results$effects[-1]) # -1 to avoid the effect
qq <- qqnorm(effects) 
text(qq$x, qq$y, labels = names(effects))
```


MODEL ADEQUACY
```{r}
#find residual
residuals <- resid(results)
residuals
```

```{r}
predicted= predict(results)
predicted
```


NORMAL 

```{r}
library(ggplot2)
library(ggpubr)
ggqqplot(residuals)
```
Based on the normality of the residual plot, the residual not inline for certain values, we could say 
that the assumption of the normality is not satisfy. The graph also have an outlier


Test normaliy of the residuals using Shapiro-Wilk Test
```{r}
shapiro.test(residuals)
```
$H_{0}$: The residuals is normally distributed\
$H_{1}$: The residuals is not normally distributed\
$p-value=0.2757$\
Since ($p-value=0.2757$)$>$($\alpha=0.05$), do not reject $H_{0}$.\
At $\alpha=0.05$, The residuals is normally distributed\

CONSTANT VARIANCE

```{r}
#plot residual vs predicted
plot(predicted, residuals)
```

```{r}
plot(lm(residuals~predicted))
```

the plot show a random scattering of points above and below the reference line at a horizontal 0. It is constant variance.

INDEPENDENCE
```{r}
#plot residuals vs observations
plot(data$strength,residuals)
```

Perform Durbin-Watson test
```{r}
library(car)
```

```{r}
durbinWatsonTest(residuals)
```

```{r}
durbinWatsonTest(results)
```

$H_{0}$: There is no correlation among the residuals.\
$H_{1}$: The residuals are autocorrelated\
$p-value=0.6080$\
Since ($p-value=0.6080$)$>$($\alpha=0.05$), do not reject $H_{0}$.\
At $\alpha=0.05$, There is no correlation among the residuals.\